Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-17 manuscript.Rmd
update initialization

# Read BWR functions for Mac OS
source("/Users/beperron/Git/BibWrangleR/functions/proquestBWR.R")

@@

# Read BWR functions for Mac OS
source("/Users/beperron/Git/BibWrangleR/functions/ebscoBWR.R")

@@

```{r BGVinitialization, eval=FALSE}
rm(list=ls())  
load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")

# Load required packages
library(ggplot2)
library(dplyr)
library(gridExtra)
```

@@

source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticlesRevised.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")

combineData.f()
cleaningJournals.f()
shortArticles.f()
titleMatching.f()
otherDocuments.f()
fewArticles.f()
#save.image(file = "socialWorkHistory.Rdata")
```

>>>>

library(BibWrangleR)

@@

@@

@@

source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticlesRevised.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/requireAuthorJournalTitleYear.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")

combineData.f()
cleaningJournals.f()
shortArticles.f()
titleMatching.f()
otherDocuments.f()
requireAuthorJournalTitleYear.f()
#save.image(file = "socialWorkHistory.Rdata")
```
